Additional analysis

### 2020-01-20 README.Rmd
Add new installation instructions

Title <- "Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
Authors <- "Suparna Chaudhry and Andrew Heiss"
Year <- "2019"
```

@@

[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of Political Science • Christopher Newport University  
[Andrew Heiss](https://www.andrewheiss.com/) • Romney Institute of Public Service and Ethics • Brigham Young University

@@

1. Open the compendium as a project in RStudio (double click on `crackdownsphilanthropy.proj`).
2. Install the **pkgbuild**, **devtools**, **rstan**, and **rstantools** packages, either with RStudio's "Packages" panel or by running `install.packages(c("pkgbuild", "devtools", "rstan", "rstantools"))`
3. Due to [strange](https://github.com/stan-dev/rstantools/issues/52) [incompatibilties](https://github.com/klutometis/roxygen/issues/822#issuecomment-441425591) with **roxygen2** and **rstantools**, you need to compile the Stan C++ binary DLLs before building the actual **crackdownsphilanthropy** compendium package. Run `pkgbuild::compile_dll()` and wait a few minutes while the Stan models are built.
4. Finally, build the compendium package by clicking on the "Install and Restart" button in RStudio's "Build" panel.

>>>>

Title <- "Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
Authors <- "Suparna Chaudhry and Andrew Heiss"
Year <- "2020"
```

@@

[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of Political Science • Christopher Newport University  
[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University

@@

1. Open the compendium as a project in RStudio (double click on `crackdownsphilanthropy.proj`).

2. Install the **pkgbuild**, **devtools**, **rstan**, and **rstantools** packages, either with RStudio's "Packages" panel or by running `install.packages(c("pkgbuild", "devtools", "rstan", "rstantools"))`

3. You need to compile the Stan c++ binary DLLs before building and installing the actual  **crackdownsphilanthropy** compendium package ([see here for details about why](https://mc-stan.org/rstantools/articles/minimal-rstan-package.html#documentation)). Run these two lines in R:

    ```r
    pkgbuild::compile_dll()  # This will probably take a few minutes
    roxygen2::roxygenize()
    ```

4. Finally, build the compendium package by running this in R:

    ```r
    devtools::install(".")
    ```
